---
title: "HW03 template"
output:
  word_document: default
  pdf_document: default
  
  ### Name
---

```{r setup, include=FALSE}

library(car)
library(agricolae)
library(DunnettTests)
library(multcomp)

```

**Problem**
Field trials are central to agricultural reserach. We have provided two datasets using a standeard field design, Randomized Complete Block, for you to explore.  

**a.	State the null and alternative hypotheses for the experiment.**
**Answer:** 
Null Hypothesis: 
Alternative Hypothesis: 

**b. Write the linear model and define the components of the model.**
**recal this is the abstraction of the design**
**Answer:** 



**c.	Conduct an Analysis of Variance (ANOVA) for for two of the response variables**
```{r}
dat<- read.csv('') #read in data
head(dat)
str(dat)
```

**d.	Write out the table**
```{r}
aov.dat <- aov()
summary(aov.dat)
```


**e. Construct a table of treatment means using an appropriate mean separation procedure of your choice.**

```{r}

lsd.dat <- LSD.test() # or HSD or dunnett
bar.group()
title(cex.main=0.8,main="Impact of Planting date Yield",xlab="Planting Date",ylab="Yield")

```

**f.	Write a brief summary of the results and discuss conclusions you could draw from the data set.**
**Answer:** 








## R Markdown

